\documentclass[11pt]{letter} 
\usepackage{newcent} % Default font is the New Century Schoolbook PostScript font 
%\usepackage{helvet} % Uncomment this (while commenting the above line) to use the Helvetica font

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=10in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa

\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\newcommand{\company}{\emph{Epic}}
\newcommand{\job}{\emph{Software Developer}}
\begin{document}

\begin{letter}{
%Mrs. Jane Smith \\
%Recruitment Officer \\
%The Corporation \\
%123 Pleasant Lane \\
%City, State 12345
} 

\begin{center}
\large\bf Jie Feng \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
 (443) 996-2046 $\bullet$ jiefeng.hopkins@gmail.com \\% Your address and phone number
500\,W University Pkwy Apt 9D, Baltimore, MD21218 
\end{center} 
\date{}
\signature{Jie Feng} % Your name for the signature at the bottom

\vspace*{-40pt}
\opening{Dear Hiring Professional,} 
I'm Jie Feng. And I went for \emph{On-Site interview} of \textbf{\company} last semester.  Before my talking about the interview, let me first briefly introduce myself:

I am currently a graduate student at Johns Hopkins University majoring security informatics and my expected graduation is December of this year.
I am seeking an \job{} internship position for this summer 2014.  

%\item Excellent algorithm design and implementation skills, with 1500+ pieces of algorithm programs written so far.

%My understanding of Bloomberg is a financial software, data and media company who has the mission to help different parties make smarter, faster, more profitable decisions in this fast changing global environment.  What Bloomberg means to me and what can I do for Bloomberg as a programmer? It is a very big question, but at least I got one point from this question, that is Bloomberg can give me a broad view of the world while I'm contributing to Bloomberg with my specialties. 


My most knowledgeable area is building softwares and solving problems with algorithms, which is due to my hard working
in this area in the past several years.  
I started studying algorithms and hacking algorithm problems since I was a high school kid, which was 6 years ago. 
Since then, I intermittently solved more than 1500 pieces of programs among a vast area of topics in algorithm, most of which are written with C/C++.

Algorithm studying, practicing and competing requires not only a quick and clear mind in problem solving, but also a distinguished willpower in continually trying things hard and new.
However, I went beyond that as I took algorithm hacking for fun and would enjoy every algorithm contests I have participated ever.
Very luckily, I've accomplished some remarkable performances among these contests, such as \textbf{National First Prize} in
\emph{"Lanqiao Cup"} in \emph{China}, \textbf{Bronze Medal} in \emph{ACM-ICPC}, or \textbf{42th place} among more than 4000 global contestants in a 24-hour hackthon just a few weeks ago.



In addition to my persistent commitment in algorithm, I have also led or participated in software developing in
different areas including cryptography, security, web, networking, android development and reverse engineering. 
One special project I would like to mention is the \emph{"Universal Online Examination System"}, since it was sponsored by me.
In that project, I lead my teammates, who were all sophomore students without any web developing experience before, in
building a web-based examination system. We worked hard day and night, and finally came out with a robust system which
is still well serving more than 20,000 university students now. What I've learnt most from that project is starting
something new is much harder than doing something hard, for example, hacking tricky algorithm  problems.



%I have a very good experience in implementing softwares, maybe my enclosed resume could tell you more about my skills and experiences.

Last semester, I passed every previous interviews and entered the On-Site interview  from \company{}.  
Unfortunately, I lost my phone on the plane while returning. 
What's worse, there was a heavy snow at \emph{Baltimore} and we were all preparing and having final for the next
few days. So I didn't buy a new phone immediately. As a result, I missed all phone calls from \company{} until I got
the email telling me that \company{} have already contacted me for many times.
I really apologize for what had happened. 
But I really love \company{} and \company 's Disneyland-like huge campus. 

While \company{} means a lot to me, I'm confident
I will be a valuable asset to \company{} too, which can bring a combination of extraordinary skills and passionate
dedication in daily work. I hope that \company{} could give me a second chance to further discuss my qualifications.

%I was so excited about the On-Site interview cause it's the first time for me to have interview with an American company, especially it's a giant company. Everything is new to me, as a employee of \company{}, you can imagine how I felt when I walked around \company 's Disneyland-like huge campus. I was so excited that I took pictures all along the tour with \company 's employees and I almost forgot about what I was really for on that day. I apologize for my behavior especially when I came to \company for job. 





%PARAGRAPH ONE: I am  
%State the reason for the letter, name the position or type of work you are applying for 
%and identify the source from which you learned of the opening (i.e. career development center, newspaper, employment service, personal contact).
%
%PARAGRAPH TWO: Indicate why you are interested in the position, the company, its products, services - above all, stress what you can do for the employer. If you are a recent graduate, explain how your academic background makes you a qualified candidate for the position. If you have practical work experience, point out specific achievements or unique qualifications. Try not to repeat the same information the reader will find in the resume. Refer the reader to the enclosed resume or application which summarizes your qualifications, training, and experiences. The purpose of this section is to strengthen your resume by providing details which bring your experiences to life. 
% 
%PARAGRAPH THREE: Request a personal interview and indicate your flexibility as to the time and place. Repeat your phone number in the letter and offer assistance to help in a speedy response. For example, state that you will be in the city where the company is located on a certain date and would like to set up an interview. Alternatively, state that you will call on a certain date to set up an interview. End the letter by thanking the employer for taking time to consider your credentials. 
%
\closing{Sincerely yours,}
\encl{Resume} % List your enclosed documents here, comment this out to get rid of the "encl:"

%----------------------------------------------------------------------------------------

\end{letter}

\end{document}
